### 2014-10-28 contract-language.tex
Edits

\noindent Observe that the contracts $\scc$, $\ccc$ and $\ecc$ are themselves
totally ordered with respect to the $\le$ relation: $\ecc \le \ccc \le \scc$.
This concurs with the intuition that any contract satisfiable under $\ecc$ or
$\ccc$ is satisfiable under $\scc$, and any contract that is satisfiable under
$\ecc$ is satisfiable under $\ccc$. Nonetheless, we determine the class of a
contract based on the \emph{weakest} guarantee (among $\ecc$, $\ccc$, and
$\scc$) required to satisfy the contract.

@@

The classification scheme is presented formally in Figure~\ref{sem:classify}.
Along with three straightforward rules that classify contracts into consistency
classes, the classification scheme also presents a rule that judge
well-formedness of a contract. A contract is well-formed if and only if it is
satisfiable under $\scc$ - the strongest possible consistency guarantee any
store can provide. The $\le$ relation used by the rules is defined formally
below:

@@

The $\Delta$ referred in the above defintion captures assumptions about the
nature of primitive relations, such as $\Rvis$ and $\Rso$ are irreflexive, and
the happens-before relation $\hbZ$ is acyclic, preventing thin-air reads.
\KC{Ideally, we need to list all the axioms somewhere.}

>>>>

@@

\noindent Observe that the contracts $\scc$, $\ccc$ and $\ecc$ are themselves
totally ordered with respect to the $\le$ relation: $\ecc \le \ccc \le \scc$.
This concurs with the intuition that any contract satisfiable under $\ecc$ or
$\ccc$ is satisfiable under $\scc$, and any contract that is satisfiable under
$\ecc$ is satisfiable under $\ccc$. Nonetheless, we determine the class of a
contract based on the \emph{weakest} guarantee (among $\ecc$, $\ccc$, and
$\scc$) required to satisfy the contract. The classification scheme is
presented formally in Figure~\ref{sem:classify}. The $\le$ relation used by the
rules is defined formally below:

@@

The $\Delta$ referred in the above defintion captures assumptions about the
nature of primitive relations, such as $\Rvis$ and $\Rso$ are irreflexive, and
the happens-before relation $\hbZ$ is acyclic, preventing thin-air reads.
\KC{Ideally, we need to list all the axioms somewhere.} Along with three
straightforward rules that classify contracts into consistency classes, the
classification scheme also presents a rule that judge well-formedness of a
contract. A contract is well-formed if and only if it is satisfiable under
$\scc$ - the strongest possible consistency guarantee any store can provide.
